Delone lattice studies in \CIII, the space of three complex variables

### 2023-05-31 C3/C3.tex

 \{(-\si,~\siv-\si ),~(\siii+\si,~\sii+\si), (\svi+\si,~\sv+\si)\}\\
 =
\begin{tabular}{ccc}
	 $\begin{bmatrix}
 	~\\~\\~\\
 \end{bmatrix}$

@@

Here, one of the four possible result vectors has been chosen 
(arbitrarily).

@@

@@

>>>>

 \{(-\si,~\siv-\si ),~(\siii+\si,~\sii+\si), (\svi+\si,~\sv+\si)\}\\
 =
\begin{tabular}{ccc}

 	RedMat

@@

We need to solve for RedMat.
Here, one of the four possible result vectors has been chosen 
(arbitrarily).

@@

\subsection{Example of use}

To demonstrate the application of the above matrices,
example C++ code was written to create matrices of operators;
see the supplementary material for the code or the complete
library reference in the Availability of Code below.

Create a \CIII{} vector c3 with
the values \{(1,2),(3,4),(5,6)\} (which does not
correspond to a valid unit cell). Multiply it by the matrix
of operators derived above.

The matrix multiply can be implemented as follows"

\begin{verbatim}
C3 C3::c3_s1(const C3& a) {
    C3 c;
    c[0] = c3_Minus_Real(a[0]);
    c[1] = c3_Plus_Real(a[0]) + c3_Real(a[1]) +
        c3_I_Times_Real(a[2]);
    c[2] = c3_Plus_Real(a[0]) + c3_Imag(a[1]) +
        c3_I_Times_Imag(a[2]);
    return c;
}
\end{verbatim}

Therefore, RedMat = \\
\begin{center}
	$\begin{bmatrix}
	\Minus{}_r	& 0			& 0 \\
	\Plus{}_r	&  \Real{}	& \textrm{i}\Real{} \\
	\Plus{}_r	& \Imaginary{}		&\textrm{i}\Imaginary{}
\end{bmatrix}	$
\end{center}

For example:

\begin{center}
\{(-1.000,1.000) (4.000,6.000) (5.000,7.000)\} =\\
$\begin{bmatrix}
	\Minus{}_r	& 0			& 0 \\
	\Plus{}_r	&  \Real{}	& \textrm{i}\Real{} \\
	\Plus{}_r	& \Imaginary{}		&\textrm{i}\Imaginary{}
\end{bmatrix}	$
$\begin{Bmatrix}
	(1,2)\\
	(3,4)\\
	(5,6)
\end{Bmatrix}$\\

\end{center}

which can be verified by hand.

@@

\begin{figure}
	\includegraphics[width=1.0\textwidth]{19_57}
	label{19\_57}
	\caption{The PLA2 unit cells, Niggli-reduced, and five copies were perturbed 10\%
		orthogonally to \SVI{} vector, followed by Niggli reduction.}
\end{figure}
